### 2022-11-05 doc/src/MSLevel.tex
Clarify *topi CSRs
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

The {\RISCV} Privileged Architecture ensures that, when the value
of \z{mtopi} is not zero, a trap is taken to \mbox{M-mode} for the
interrupt indicated by field IID if either the current privilege
mode is~M and the MIE bit in CSR \z{mstatus} is set, or the current
privilege mode has less privilege than \mbox{M-mode}.
The trap itself does not cause the value of \z{mtopi} to change.

@@

The {\RISCV} Privileged Architecture ensures that, when the value
of \z{stopi} is not zero, a trap is taken to \mbox{S-mode} for the
interrupt indicated by field IID if either the current privilege
mode is~S and the SIE bit in CSR \z{sstatus} is set, or the current
privilege mode has less privilege than \mbox{S-mode}.
The trap itself does not cause the value of \z{stopi} to change.

>>>>

The value of \z{mtopi} is not affected by
the global interrupt enable MIE in CSR \z{mstatus}.

The {\RISCV} Privileged Architecture ensures that, when the value
of \z{mtopi} is not zero, a trap is taken to \mbox{M-mode} for the
interrupt indicated by field IID if either the current privilege
mode is~M and \z{mstatus}.MIE is one, or the current
privilege mode has less privilege than \mbox{M-mode}.
The trap itself does not cause the value of \z{mtopi} to change.

@@

The value of \z{stopi} is not affected by
the global interrupt enable SIE in CSR \z{sstatus}.

The {\RISCV} Privileged Architecture ensures that, when the value
of \z{stopi} is not zero, a trap is taken to \mbox{S-mode} for the
interrupt indicated by field IID if either the current privilege
mode is~S and \z{sstatus}.SIE is one, or the current
privilege mode has less privilege than \mbox{S-mode}.
The trap itself does not cause the value of \z{stopi} to change.

### 2022-11-05 doc/src/VSLevel.tex
Clarify *topi CSRs
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Virtual supervisor top interrupt CSR (\zSafe{vstopi})}

@@

Whenever the value of CSR \z{vstopi} is not zero, if either the current
privilege mode is \mbox{VS-mode} and the SIE bit in CSR \z{vsstatus}
is set, or the current privilege mode is \mbox{VU-mode}, a trap is
taken to \mbox{VS-mode} for the interrupt indicated by field IID of
\z{vstopi}.

>>>>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Virtual supervisor top interrupt CSR (\zSafe{vstopi})}
\label{sec:vstopi}

@@

The Advanced Interrupt Architecture modifies the standard
{\RISCV} Privileged Architecture such that an interrupt
is pending at VS level if and only if \z{vstopi} is not zero.
CSRs \z{vsiph}/\z{vsip} and \z{vsieh}/\z{vsie} do not by themselves
determine whether a VS-level interrupt is pending, though
they may do so indirectly through their effect on \z{vstopi}.

Whenever \z{vstopi} is not zero, if either the current
privilege mode is \mbox{VS-mode} and the SIE bit in CSR \z{vsstatus}
is one, or the current privilege mode is \mbox{VU-mode}, a trap is
taken to \mbox{VS-mode} for the interrupt indicated by field IID of
\z{vstopi}.
